Characterization and Photometric Performance of the Hyper Suprime-Cam Software Pipeline.

### 2017-04-27 draft/ms_v5.tex
HSC overview

    %% Basic
    Taking advantage of the new prime focus camera on the 8.2--m Subaru telescope,
    the ambitious HSC survey consists of three layers: Wide, Deep, and UltraDeep.
    The Wide layer will map a total of ${\sim}1400$ deg$^2$ of sky in five broad bands
    ($grizy$; Kawanomoto\etal in prep.).
    The Deep (four separated fields; ${\sim}27$ deg$^2$) and UltraDeep (two separated
    fields; ${\sim}3.5$ deg$^2$) layers use a few additional narrow-band filters
    and employ a slightly different surveying strategy.
    Strauss\etal (in prep.) describes the HSC survey in more detail, and identifies the
    HSC collaborators.

    The HSC camera (\citealt{Miyazaki2012}) is made up of 124 full-depletion thick
    CCDs: 112 for science and another 12 for guiding and focusing.
    The camera has a circular FoV with a 1.5 deg diameter.
    Each CCD contains 2048$\times$4096 pixels and the sizes of pixels are 0.168\asec{}.

    In February 2017, the HSC collaboration released the first 1.7 years of data to
    the public (DR1;
    \citealt{HSCDR1})\footnote{\texttt{https://hsc-release.mtk.nao.ac.jp }}.
    For our work, we focused on data from the Wide layer as they relate to key
    scientific goals of the HSC survey, which include weak lensing cosmology, galaxy 
    evolution, and studies of galaxy clusters. 
    The Wide layer data in DR1 correspond to ${\sim}108$ deg$^2$ spread over 
    six fields (XMM--LSS, GAMA09H, WIDE12H, GAMA15H, HECTOMAP, and VVDS)
    \footnote{A small AEGIS field is also observed for calibration purposes.}.
    Except for the HECTOMAP field, the regions are all close to the equator.
    In the Wide layer, the $g$ and $r$ bands have 10 minute exposures broken into 
    four dithers.  
    The $i$, $z$, and $y$ bands have 20 minute exposures broken into six dithers. 
    The survey prioritizes the observations so that the $i$-band has the best seeing 
    conditions to improve galaxy shape measurements for weak lensing science. 
    The $i$ band data in the Wide layer reach a $5\sigma$ point source limiting 
    magnitude of $i{\sim} 26.4$ mag and have a median seeing with 
    FWHM${\sim}0.6$\asec{}. 
    \citealt{HSCDR1} provides details on the first data release and data status.

@@

%% ------------------------------------------------------------------------------------ %%
\section{The HSC Data Reduction Pipeline}
    \label{ssec:hscpipe}

@@

        \item \textbf{Single-\texttt{Visit~}Processing}:
            Each individual exposure is called a \term{Visit} and is assigned
            an even integer.
            After initial data screening (considering the background level, seeing, 
            and transparency Furusawa\etal in prep.), \hscpipe{} subtracts overscan, 
            bias, and dark frames, and performs flatfielding to the single CCD images.
            During this step, \hscpipe{} also generates variance and mask images, 
            subtracts the background, and provides initial astrometric and photometric
            calibrations. 
            \synpipe{} uses the spatially varying PSF models, photometric zeropoints, 
            and the World Coordinate System (WCS; \citealt{WCS1, WCS2})
            corrected for optical distortion provided by \hscpipe{}.

        \item \textbf{Multi-\visit{} Processing}:
            After single-\visit{} processing, \hscpipe{} warps and mosaics the
            reduced CCD images into much deeper \coadd{} images while improving
            the astrometric and photometric calibrations via processes similar to
            the \"{u}ber-calibration in the Sloan Digital Sky Survey (SDSS)
            \citep{Padmanabhan2008}.
            \textbf{\synpipe{} will use these improved calibrations.}
            \hscpipe{} organizes these \coadd{} images into equiareal rectangular
            regions, or \tracts{}, which are predefined as iso-latitude tessellations.
            One \tract{} covers approximately $1.7\times 1.7$ degrees$^2$ and
            adjacent \tracts{} overlap each other by ${\sim}1$\amin{}.
            Each \tract{} is further divided into $9\times9$ \texttt{Patches}.
            A \texttt{Patch} is a $4200\times4200$ pixels rectangular region, and
            adjacent \texttt{Patches} overlap each other by 100 pixels.

@@

        \item \textbf{HSC Photometry}:
            The multi-band catalogs generated by \hscpipe{} contain various types of 
            photometric measurements (see \citealt{HSCDR1} for details). 
            Here, we focus on characterizing the the \forced{} \texttt{psf} and 
            \cmodel{} photometry. 
            The \texttt{psf} photometry should provide the most appropriate magnitudes 
            and colors for point sources, while the \cmodel{} should be used for 
            galaxies. 
            The HSC \cmodel{} algorithm is described in Bosch\etal, in prep. and is an
            improved version of the SDSS \cmodel{} magnitude (\citealt{Lupton2001, 
            Abazajian2004}). 
            The HSC \cmodel{} fits objects using both a de~Vaucouleurs and an 
            exponential profiles taking into account the smearing by the PSF.  
            \cmodel{} then linearly combines the two results to find the best fit to 
            the galaxy image. 
            \cmodel{} magnitudes are designed to yield accurate fluxes and colors for 
            galaxies. 
            Star--galaxy separation is performed based on the difference between 
            \texttt{psf} and \cmodel{}{} magnitudes.

@@

    DR1 data quality has been vetted in \citet{HSCDR1} by cross-checking with the 
    Panoramic Survey Telescope and Rapid Response System (Pan-STARRS) 1 imaging survey
    (\citealt{Schlafly2012, Tonry2012, Magnier2013}) to examine the behavior of the 
    stellar sequence.
    Generally speaking, the PSF photometry is accurate at the 1--2\% level for bright 
    stars, and the astrometry is accurate to ${\sim}10$ and 40 max internally and 
    externally.

@@

        \item \textbf{Realistic Images}:
            Instead of using a fully generative approach to simulate full HSC-like
            images from the ground up (e.g., \citealt{Chang2015}), \synpipe{} injects
            synthetic objects into real HSC images so that all the realistic
            features of the real data (e.g., blended objects; proximity to bright
            objects, bleeding trails, other optical artifacts can be included in the
            test.
            The impact of these features can be important for studies that care about 
            completeness and the selection function.
            In \synpipe{}, point sources are simulated using the HSC PSF model,
            and a realistic galaxy model is created by the modular galaxy image
            simulation toolkit, \galsim{} (\citealt{Rowe2015})
            \footnote{\texttt{https://github.com/GalSim-developers/GalSim}}.

@@

    \bibitem[Aihara et al.(2017)]{HSCDR1} Aihara, H., Armstrong, R., Bickerton, S.,
             et al.\ 2017, arXiv:1702.08449

>>>>

%% ------------------------------------------------------------------------------------ %%
\subsection{Status of the Survey}
    \label{ssec:ssp}

    %% Basic
    Taking advantage of the new prime focus camera on the 8.2--m Subaru telescope,
    the ambitious HSC survey consists of three layers: Wide, Deep, and UltraDeep.
    The Wide layer will map a total of ${\sim}1400$ deg$^2$ of sky in five broad bands
    ($grizy$; Kawanomoto\etal in prep.).
    The Deep (four separated fields; ${\sim}27$ deg$^2$) and UltraDeep (two separated
    fields; ${\sim}3.5$ deg$^2$) layers use a few additional narrow-band filters
    and employ a slightly different surveying strategy.
    \citet{HSCOverview} describes the HSC survey in more detail, and identifies the
    HSC collaborators.

    The HSC camera (\citealt{Miyazaki2012}) is made up of 124 full-depletion thick
    CCDs: 112 for science and another 12 for guiding and focusing.
    The camera has a circular FoV with a 1.5 deg diameter.
    Each CCD contains 2048$\times$4096 pixels and the sizes of pixels are 
    0.168\asec{}.
    For more details about the HSC camera, please see Miyazaki\etal (in prep.).

    In February 2017, the HSC collaboration released the first 1.7 years of data to
    the public (DR1;
    \citealt{HSCDR1})\footnote{\texttt{https://hsc-release.mtk.nao.ac.jp }}.
    For our work, we focused on data from the Wide layer as they relate to key
    scientific goals of the HSC survey, which include weak lensing cosmology, galaxy 
    evolution, and studies of galaxy clusters. 
    The Wide layer data in DR1 correspond to ${\sim}108$ deg$^2$ spread over 
    six fields (XMM--LSS, GAMA09H, WIDE12H, GAMA15H, HECTOMAP, and VVDS)
    \footnote{A small AEGIS field is also observed for calibration purposes.}.
    Except for the HECTOMAP field, the regions are all close to the equator.
    In the Wide layer, the $g$ and $r$ bands have 10 minute exposures broken into 
    four dithers.  
    The $i$, $z$, and $y$ bands have 20 minute exposures broken into six dithers. 
    The survey prioritizes the observations so that the $i$-band has the best seeing 
    conditions to improve galaxy shape measurements for weak lensing science. 
    The $i$ band data in the Wide layer reach a $5\sigma$ point source limiting 
    magnitude of $i{\sim} 26.4$ mag and have a median seeing with 
    FWHM${\sim}0.6$\asec{} in the $i$ band. 
    \citealt{HSCDR1} provides details on the first data release and data status.

@@

%% ------------------------------------------------------------------------------------ %%
\subsection{The HSC Data Reduction Pipeline}
    \label{ssec:hscpipe}

@@

        \item \textbf{Single-\texttt{Visit~}Processing}:
            Each individual exposure is called a \term{Visit} and is assigned
            an even integer.
            After initial data screening (considering the background level, seeing, 
            and transparency Furusawa\etal in prep.), \hscpipe{} subtracts overscan, 
            bias, and dark frames, and performs flatfielding to the single CCD images.
            During this step, \hscpipe{} also generates variance and mask images, 
            subtracts the background, and provides initial astrometric and photometric
            calibrations. 
            The photometric calibration is based on data from the Panoramic Survey 
            Telescope and Rapid Response System (Pan-STARRS) 1 imaging survey 
            (\citealt{Schlafly2012, Tonry2012, Magnier2013}).
            \synpipe{} uses the spatially varying PSF models, photometric zeropoints, 
            and the World Coordinate System (WCS; \citealt{WCS1, WCS2})
            corrected for optical distortion provided by \hscpipe{}.

        \item \textbf{Multi-\visit{} Processing}:
            After single-\visit{} processing, \hscpipe{} warps and mosaics the
            reduced CCD images into much deeper \coadd{} images while improving
            the astrometric and photometric calibrations via processes similar to
            the \"{u}ber-calibration in the Sloan Digital Sky Survey (SDSS)
            \citep{Padmanabhan2008}.
            \synpipe{} will use these improved calibrations.
            \hscpipe{} organizes these \coadd{} images into equiareal rectangular
            regions, or \tracts{}, which are predefined as iso-latitude tessellations.
            One \tract{} covers approximately $1.7\times 1.7$ degrees$^2$ and
            adjacent \tracts{} overlap each other by ${\sim}1$\amin{}.
            Each \tract{} is further divided into $9\times9$ \texttt{Patches}.
            A \texttt{Patch} is a $4200\times4200$ pixels rectangular region, and
            adjacent \texttt{Patches} overlap each other by 100 pixels.

@@

        \item \textbf{HSC Photometry}:
            The multi-band catalogs generated by \hscpipe{} contain various types of 
            photometric measurements (see \citealt{HSCDR1} for details). 
            Here, we focus on characterizing the the \forced{} \texttt{psf} and 
            \cmodel{} photometry. 
            The \texttt{psf} photometry should provide the most appropriate magnitudes 
            and colors for point sources, while the \cmodel{} should be used for 
            galaxies.

                \item \hscpipe{} uses matched-filter method to derive PSF magnitude 
                    with the centroid fixed. 
                    The algorithm matches the image of a star with the PSF model 
                    multiplied by an amplitude. 
                    This amplitude parameter is estimated via the inner product of 
                    the image and PSF model after shifting the model to the centroid 
                    of the star, then divide by the effective area of the PSF model.

                \item The HSC \cmodel{} algorithm is described in Bosch\etal (in prep), 
                    and is based on the version for the SDSS \cmodel{} magnitude 
                    (\citealt{Lupton2001, Abazajian2004}). 
                    It fits objects using both a de~Vaucouleurs and an exponential 
                    profiles convolved with the PSF model.  
                    \cmodel{} then linearly combines the two results to find the best 
                    fit to the galaxy image. 
                    \cmodel{} magnitudes are designed to yield accurate fluxes and 
                    colors for galaxies. 
                    Star--galaxy classification is also performed based on the 
                    difference between \texttt{psf} and \cmodel{}{} magnitudes.

@@

    DR1 data quality has been vetted in \citet{HSCDR1} by cross-checking with the 
    Pan-STARRS 1 imaging survey to examine the behavior of the stellar sequence.
    Generally speaking, the PSF photometry is accurate at the 1--2\% level for bright 
    stars, and the astrometry is accurate to ${\sim}10$ and 40 max internally and 
    externally.

@@

        \item \textbf{Realistic Images}:
            Instead of using a fully generative approach to simulate full HSC-like
            images from the ground up (e.g., \citealt{Chang2015}), \synpipe{} injects
            synthetic objects into real HSC images so that all the realistic
            features of the real data (e.g., blended objects; proximity to bright
            objects, bleeding trails, other optical artifacts) can be included in the
            test.
            The impact of these features can be important for studies that care about 
            completeness and the selection function.
            In \synpipe{}, point sources are simulated using the HSC PSF model,
            and a realistic galaxy model is created by the modular galaxy image
            simulation toolkit, \galsim{} (\citealt{Rowe2015})
            \footnote{\texttt{https://github.com/GalSim-developers/GalSim}}.

@@

    \bibitem[Aihara et al.(2017a)]{HSCDR1} Aihara, H., Armstrong, R., Bickerton, S.,
             et al.\ 2017, arXiv:1702.08449

    \bibitem[Aihara et al.(2017b)]{HSCOverview} Aihara, H., Armstrong, R., 
             Bickerton, S., et al.\ 2017, arXiv:1702.08449
